Viscous Transport in Eroding Porous Media

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. }

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.45 \textwidth]{./figs/velocity_loc}
\includegraphics[width = 0.45 \textwidth]{./figs/tort_local}\\

\includegraphics[width = 0.45 \textwidth]{./figs/tortU_local}
\includegraphics[width = 0.45 \textwidth]{./figs/uminDumax}

\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{center}
\end{figure}

>>>>

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity, namely, $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section at x=-1 and y in [-1,1]. The velocity is continuous along the cross section and acting as several Poiseuille flows. This velocity graph is different from the one in~\cite{matyka2008tortuosity} since we choose our cross section to be the beginning of the flow before the fluid touches any body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity $\tau$ of the tracers at the cross section. This graph is not continuous and the jumps in $\tau$ mean that the initial neighbor tracers have been seperated by the bodies.

In Fig.~\ref{fig:Eroding20tort}(c)
In Fig.~\ref{fig:Eroding20tort}(d) }

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tortU_local}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{figure}
